%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{UJJWAL AGGARWAL}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{\\LinkedIn : www.linkedin.com/in/ujjwal-aggarwal-a88992148
\\Github : https://github.com/ujjwal123aggarwal\\
}
\address{ujjwal.aggarwal10@gmail.com \\(+91) 9811701135\\}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{VISION}
{\sl "Don't be stagnant , Keep moving" }

\section{EDUCATION}
\textbf{Bharati Vidyapeeth's College of Engineering}, New Delhi\\
{\sl Bachelor of Technology (B. Tech)}, Electronics and Communication Engineering(ECE)\\
Expected July, 2021


\textbf{Mount Abu Public School}, New Delhi \\
{\sl Class XII (Senior Secondary Examination)}, CBSE\\
March 2017
\hfill Aggregate 84.5\%

\textbf{Mount Abu Public School}, New Delhi \\
{\sl Class X (Secondary Examination)}, CBSE\\
March 2015
\hfill CGPA: 10/10



%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{TECHNICAL\\SKILLS}

\textbf{Languages : } C, Embedded C / Arduino, Python
\\
\textbf{Technologies :} Embedded Systems, Robotics, Augmented Reality, \\               Machine Learning(Mediocre),Internet of Things(Mediocre),\\ Visible Light Communication(Mediocre)
\\
\textbf{Tools/Framework : } Arduino IDE, AVR studio, Unity, Proteus, Libre Pilot,
ISIS 7 professional,OpenCV(library),ARES 7,
Sketchup Make, GNU SIM8085S
\\
\textbf{Development Boards : }Arduino Boards, Atmega16, STM32, CC3D Flight controller

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{PATENT}

Object Location and Precision Guidance for the blind\\Intellectual Property India Serial No. 201911002066


\section{EXPERIENCE}

\textbf{ACADEMY OF ROBOTICS : Project Intern \hfill{July 19 - Aug 19}\\}
\normalfont{Making, Learning based Projects using Embedded Systems and Augmented Reality like Drones, AR designing etc}
\\
\textbf{MSSL : Trainee \hfill{June 19 - July 19}\\}
\normalfont{Embedded Systems, Industrial Controllers, Automobile }
\\
\textbf{Cyborg Labs : Trainee \hfill{June 18 - July 18}\\}
\normalfont{Embedded Systems, Robotics, PCB designing}

\section{POSITION \\TO BE\\RESPONSIBLE}

\textbf{BVP IEEE : MAKERS Head \hfill{July 19 - Present}\\}
\normalfont{Makers is a Project Based Sub-Society under BVP IEEE , Teaching and conducting Workshops related to Robotics, Visible Light Communication, Wearable Technologies.}
\\
\textbf{BVP IEEE : Student Representative \hfill{July 18 - July 19}\\}
\normalfont{A Bridge between the society and its fellow student members. Includes handling technical projects as well as management process.  }
\\
\textbf{Head Event-Manager : PLAN FOR INDIA\hfill{April 19}\\}
\normalfont{A Business-Technical Competition}


\section{PROJECTS}

\employer{}
\location{}
\title{\textbf{\underline{EASYWAY} \hfill Aug 2019}}
\begin{position}
%\begin{itemize}
A Software version of our similar project Go-connect(2018) Solving problem of Traffic congestion.
%\end{itemize}
\begin{itemize}
\item \textbf{Technology/Tools:} Mobile application, Communication
\end{itemize}
%\begin{itemize}
%\item \textbf{Link :} 
%\end{itemize}
\end{position}

\employer{}
\location{}
\title{\textbf{\underline{NURSE-JOY}\hfill July 2019}}
\begin{position}
% \begin{itemize}
A Humanoid Bot Wireless controlled by a jacket designed to assist nurses in ICUs.
% \end{itemize}
\begin{itemize}
\item \textbf{Technology/Tools:} Robotics, Embedded Systems, Android, Communication.
\end{itemize}
%\begin{itemize}
%\item \textbf{Link :} 
%\end{itemize}
\end{position}

\employer{}
\location{}
\title{\textbf{\underline{CISCO-APP}\hfill March 2019}
 }
\begin{position}
% \begin{itemize}
Solving Queue analysis problem by CISCO using mobile application and         CISCO meraki camera.
% \end{itemize}
\begin{itemize}
\item \textbf{Technology/Tools:} Computer vision , Mobile Application
\end{itemize}
%\begin{itemize}
%\item \textbf{Link :} 
%\end{itemize}
\end{position}

\employer{}
\location{}
\title{\textbf{\underline{X-QUADCOPTER} \hfill Jan 2019}
 }
\begin{position}
% \begin{itemize}
Using CC3D flight controller and brushless DC motors with Geofencing system through external GPS modules.
% \end{itemize}
\begin{itemize}
\item \textbf{Technology/Tools:} Sensor Embedded, Robotics, Communication
\end{itemize}
%\begin{itemize}
%\item \textbf{Link :}
%\end{itemize}
\end{position}

\employer{}
\location{}
\title{\textbf{\underline{GRIPPLE} \hfill Oct  2018}
 }
\begin{position}
% \begin{itemize}
A wearable band for blinds which uses Object detection Algorithms to detect a surrounding object and then uses a haptic feedback mechanism to guide the person towards that Object.
% \end{itemize}
\begin{itemize}
\item \textbf{Technology/Tools:} Robotics,Embedded Systems, Communication, Deep Learning
\end{itemize}
%\begin{itemize}
%\item \textbf{Link :} 
%\end{itemize}
\end{position}

\employer{}
\location{}
\title{\textbf{\underline{GOCONNECT} \hfill Aug  2018}
 }
\begin{position}
% \begin{itemize}
A road transport system to provide convenient and safe daily travel.
% \end{itemize}
\begin{itemize}
\item \textbf{Technology/Tools:} Sensor Embedded Systems, IOT, App Development.
\end{itemize}
%\begin{itemize}
%\item \textbf{Link :}https://www.youtube.com/watch?v=EWrsB4joozQ
%\end{itemize}
\end{position}


\section{ACHIVEMENTS}
\par
%\normalfont{.}
\\\normalfont{\textbullet{} \textbf{WINNER of SMART INDIA HACKATHON(Hardware Edition)} for\\ making Nurse Joy at SRM University, Chennai.}
\\
\normalfont{\textbullet{} \textbf{WINNER of TECHQUEST} for making GoConnect at IGDTUW, New Delhi.
\\
\normalfont{\textbullet{} Secured among Top Teams in \textbf{Hack-a-Bit} at BIT mesra, mesra and \textbf{Pune Smart City Hackathon} at Pune University, Pune.
\\
\normalfont{\textbullet{} Worked for Cisco Systems and Cisco Meraki in \textbf{SMART INDIA HACKATHON(Software Edition)} at SBCE, Kerala.
\\




\section{VOLUNTEER}
\par
\\
\normalfont{\textbullet{} PyData Conference 2019}\\
\normalfont{ \textbullet{} SWACHH BHARAT internship }\\
\normalfont{ \textbullet{} IYM(Igniting young Minds)}\\
\normalfont{\textbullet{} LFT(Leaders For Tomorrow)}\\
\normalfont{\textbullet{} BVP-IEEE}


%-------------------------------------------------------------------------------


\end{resume}
\(\)\end{document}